---
title: "Decomposition of Sequences into Slices "
author: "Sam"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Decomp}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Decomposition of Sequences into Slices
The input to the routine \code{decomp} should be a vector containing a monotonically increasing 
sequence of positive integers. Error checking is not comprehensive. Any sequence that contains 
zero or has repeated elements is likely to result in a segfault. 

```{r}
library(rSeqSliceDecomp)
x <- c(2, 4, 6, 8, 10, 15, 20, 25, 30)
s <- decomp(x)
s
```

The algorithm finds the longest slice and adds it to the output set. When no slice 
longer than three remains, it groups the remaining points in pairs and (if an 
odd number of points remain) one singleton.

```{r}
library(rSeqSliceDecomp)
x <- c(10, 11, 12, 20, 21, 22, 30, 31, 32)
s <- decomp(x)
s
x <- c(10, 11, 12, 20, 21, 22, 30, 31, 32, 40, 41, 42)
s <- decomp(x)
s
```

### Note: R slices and numpy slices
R slices and numpy slices differ in two ways. (1) R indices begin at 1 and 
numpy indices begin at 0 and (2) if `stop-start` is a multiple of `step`,
R slices include `stop` and numpy slices do not.

Since this is an R package, all slices are R slices. To use them with 
`h5pyd` it will be necessary to modify them.
